Apartment Evaluations Have Been Beneficial to the City of Toronto

### 2022-02-07 outputs/paper/paper.Rmd
finishing touches

mut_data <- data %>%
  mutate(score_category =
           case_when(SCORE <= 50 ~ "<=50",
                     SCORE <= 65 ~ "51-65",
                     SCORE <= 85 ~ "66-85",
                     SCORE <= 100 ~ "86-100"),
         score_category = factor(score_category,
                                 levels = c("<=50",
                                            "51-65",
                                            "66-85",
                                            "86-100"
                                            )
                                 )
         )

view(data)
head(mean_wards)
view(mean_wards)
```

>>>>

mut_data <- data %>%
  mutate(score_category =
           case_when(SCORE <= 50 ~ "<=50",
                     SCORE <= 65 ~ "51-65",
                     SCORE <= 85 ~ "66-85",
                     SCORE <= 100 ~ "86-100"),
         score_category = factor(score_category,
                                 levels = c("<=50",
                                            "51-65",
                                            "66-85",
                                            "86-100"
                                            )
                                 )
         )
```
